Legends for Tables

### 2019-05-14 Manuscript/Tables/table_legends.Rmd
editted legends

>>>>

**Table 2. Jaccard Indices.** The median (range) Jaccard index illustrating the pairwise similarity between annotations within specific groups, including chromatin segmentation states, histone modifications, and transcription factor binding sites. The Jaccard Index measures the ratio of the number of intersecting base pairs between any two sets, to the number of base pairs in the union of the two sets. The number of cell line specific annotations included within each group is also provided.
